The expected shape of the Milky Way's Dark Matter halo

### 2018-09-18 Paper/paper.tex
column width

Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos. Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}. Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-). Other works of this type?\\

While these studies are elucidating about dynamical aspects that may play important roles in the rounding of the DM halo shape, they do not follow baryons in the whole cosmological context. Abadi-Navarro and Bryan-Kay studied the evolution of galaxies in hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\

@@

These halos were randomly selected from a sample of the most isolated quartile of halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass is defined as the mass enclosed within the virial radius $R_{200}$ at which the density becomes 200 times the critical density of the universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated with the (AREPOOO HERE) by increasing the mass resolution of the particles belonging to them and diminishing the resolution of the rest of the particles.\\

Various versions of each halo were modelled with different degrees of realism. All 30 halos were simulated within a level-4-degree of resolution defined for Aquarius simulations corresponding to $\tilde 3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5 M_\odot$. The principal details of each of these halos are consigned on the table \ref{tab:level4}. From these halos, 6 of them where re-simulated at level 3 (higher) resolution taking into account a spatial factor of 2 in each dimension. For more information about level 3 halos, their details are printed on table \ref{tab:level3}. Furthermore, fore each halo in each level of resolution there are two versions of the simulation. One of tracks the evolution of DM-only particles while the remaining one evolves DM and baryions with magneto-hydrodynamical (MHD) physics, including DM.\\

@@

There is no trivial way to calculate the DM halo shape at a determined radius due to the discretization of particles. For practical effects, observational models focus on the shape of the DM isopotential \cite{isopotential} or isodensity \cite{isodensity} contours. In cosmological simulations, it is preferred to work with the isodensity contours which is directly calculated from particle positions. However, these density contours are not smooth and are very sensitive to the presence of small satelites \cite{Springel Isodensity}. For this reason we determine the shape taking into account volume-enclosed particles, rather than shell-enclosed. While this approach allows the cumulative influence of outter shells on the outter shapes, it has been demonstrated for DM-only simulations that this effect becomes important only for big radii \cite{vera-Ciro aquarius}.  We therefore follow the method of \cite[Allgood et al. 2006]{Allgood_et_al._2006} that consits in the use of the reduced inertia tensor,   \\

@@

The diagonalization of this tensor yields the principal axes of the structure as well as the eigen-quantities which are proportional to the squared principal axes $a>b>c$. We start our calculations taking into account particles within a sphere of radius $R$ and then recharacterize the triaxial parameters by taking into account particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$ are the previously calculated axial ratios. We repeat this process until the average deviation of semi-axes is less than $10^{-6}$.\\

\section{Results}
For convergence reasons and seeking to make our results observation-comparable, we restrict the sampling of the ellipsoidal parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS). All our results make use of this reference radius unless strictly stated otherwise.\\

\subsection{The radial tendency of axial ratios}
To have a more complete picture about the effect of baryons on the DM halo shape, we begin by verifying/understanding the radial evolution (dependence?) of the shape. In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to (the gravitational effect of inner shells?) \citep{Vera-Ciro et al. 2012}. A graphic example of this rounding can be checked on figure \ref{fig:slices}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal. Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity on the outerskirts of the halo. As a representative sample of this relations, we show on figure \ref{fig:DM relation} the evolution, for a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.\\

@@

We found that most halos exhibit a monotonically-increasing somewhat steady tendency of its axial ratios $b/a,c/a$  with radius, which is well exemplified on figure \ref{fig:DM_MHD}. There are some special cases in which fluctuations of the local DM density field affects this relation, but in average, this monotonic and steady tendency is clear and can be consulted on table \ref{table:DM table}. To ilustrate the average behavior, as well as some peculiarities, we resume the results of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where each shape represents a point in the triaxiality plane $c/a$ Vs $b/a$. Check Vera-ciro onthis.\\

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is not clear. Some studies claim that the DM halo must be oblate, at least in the vicinities of the disk, to ensure its stability \cite{disk stability}. However,)))} not much is said about its dependence with radius as previous studies focus rather on the effects of baryons on the dynamics of the halo at fixed radii. Examining the representative behaviour of a MHD halo on figure \ref{fig:DM_MHD}, some things are noticeable: first, the DM halo is almost perfectly oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its axial ratio $c/a$ does not exhibit noticeable change in the whole radial domain. (Pass from representative case to averaged values) These results are statistically supported and sumarized on table \ref{MHD table} and figure \ref{fig:Triax_MHD}\\

@@

As a check of consistency, we compare our new isopotential shape results with the analytic expression of the $(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine year]{Binney and tremaine}, taking the volume-enclosed axial ratios as an approximation for the isodensity contour ratios $q_{\rho}$. Although this analytic expression if meant to be used for logarithmic axisymmetric halos, it works well as a first approximation for nearly axisymmetric halos as those produced by our disced galaxies. We find that the difference between the real and the analytic isopotential axial ratios is not bigger than $quantity percent$. With this, we may now present on table \ref{tabe:isopotential} our observationally-comparable results for MHD halos at two important radii one corresponding to the approximate regimes where the MW DM halo is usually constrained.\\

Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?. Which models are favored?\\

@@

From the previous characterization of radial shapes it is clear that MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at every sampled radii. This can be compared on tables \ref{tabe:DM table} and \ref{tabe:MHD table} or at the representative example on figure \ref{fig:DM_MHD}. From there, it is also noticeable that the rounding effect of baryons is stronger at the disk regime, where the DM halo is almost perfectly oblate. Furthermore, MHD halos tend towards more oblate shapes (T < 0.5) despite DM halos tendency towards more prolate shapes (T>0.5).\\

This rounding effect is expected from the gravitational effect of the flattened axisymmetric galactic disk. It is also reasonable that this effect is not as strong at $\approx 100$Kpc, where the disk potential is dimmer compared to the DM halo potential. Keeping this in mind, one would expect that the rounding effect of baryons is related to some galactic parameters such as its component masses and radii. However, even for the parameter of highest correlation with this rounding effect (the baryonic fraction), the relation is not clear nor conclusive due to the dispersion from galaxy peculiarities. In figure \ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the baryonic fraction of each galaxy. Although some linear tendency is suggested qualitatively, the dispersion of the sample is very high to obtain some conclusive relation. This is an evidence that adiabatic-contraction models are not realistic as they may neglect some effects of the galaxy evolution in the whole cosmological context. \\

@@

Although the effect of the baryonic disk on the shape of the DM halo is a reasonable explanation for the rounding effect, it does not actually explain the deviation from oblateness of MHD halos at $r<10$Kpc. In other words, if the disk is perfectly axisymmetric, there must be some source of triaxiality at $r<10$Kpc to explain the low axial ratios.\\

\textit{ Talk about source of triaxiality at the inner parts of the halos (bar?). This source of triaxiality at the inner parts explains why the axial ratios are $\approx 0.95$ and not exactly $1$. We should also discuss that the decrease in the axial ratios for bigger radii may actually be bigger/steeper but it is dimmed by the contribution of inner parts.}\\
%
%\begin{figure}
%  \centering
%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
%  \hfill
%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
%  \hfill
%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$. Each dot represents a halo shape at some radius. Some observational constraints are plotted alongside our results. Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space. caption replaces title.  Present constraints representation of density)}
%  \label{fig:Triaxiality_Inner_Outer}
%\end{figure}

\subsection{The historical shape}
One of the principal motivations to study the radial dependence of the DM halo shape is that it may encode some clues about its formation history. We have already shown that DM-only halos seem to exhibit a steady and monotonous growth in its axial ratios when sampled at bigger radii. One similar effect can be found if we sample the shape at the virial radius, this time at varying redshift. It is easy to see that the axial ratios increase with decreasing redshift, which is expected by the continuous influence of the gravitational potential \cite{VeraCiro}. In figure \ref{fig:RedshiftGood} we present a representative example. \\

@@

Interestingly, these two parametic plots i.e. $(b/a,c/a)(z=0,r)$ and $(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos \ref{fig:DM Z Triax}. This means that, for DM-only halos, one can approximate its shape at higher redshift by simply sampling its current shape at a smaller radius \textbf{wording}. This relationship relies strongly on the steady and monotonous tendency of DM halos towards sphericity for bigger radii and smaller redshift.\\

@@

MHD halos, on the other hand, do not exhibit tendency towards sphericity with bigger radii, but they do get sistematically rounder at lower redshift as seen in figure \ref{fig:RedshiftGood}. This effectively vanishes this correlation as seen from a DM halo \ref{fig:MHD Z Triax}.\\

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:MHD Z Triax}

@@

One of the principal assumptions of observational models of the MW's DM halo is that its minor axis is perfectly aligned with the disk axis. Although this is a reasonable assumption to guarantee the stability of the galactic disk in simplified models of isolated galaxies, it may not be the case for galaxies evolved in the whole cosmological context nor at every radii at which the shape is sampled.\\

Therefore, it is of special interest to us to examin the strength of this alignment assumption in the context of simulations. For this purpose, we sampled the shape at 5 different radii and plotted the axial directions, as well as the disk direction in the \textbf{name} diagrams \cite{} (explain diagrams). Explain disk direction calculation.\\

@@

\section*{Acknowledgements}
This project has received funding from the European Union’s Horizon 2020 Research and Innovation Programme under the Marie Sk\l{}odowska-Curie grant agreement No 734374

>>>>

Although observations predict more symmetric halos than DM-only
simulations, there is strong evidence claiming that the presence of
baryons need/make more axisymmetrical halos. Some studies have shown
that to ensure the stability of a hydrodynamical (numeric) disk
artificially embeded in a static(non-changing) DM halo, its shape must
be axisymmetrical \cite{}. Other works have studied this rounding
effect by emulating a disk as an adiabatically growing potential
inside an N-body triaxial DM halo
\cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that
(findings of this study -debattista-). Other works of this type?

While these studies are elucidating about dynamical aspects that may
play important roles in the rounding of the DM halo shape, they do not
follow baryons in the whole cosmological context. Abadi-Navarro and
Bryan-Kay studied the evolution of galaxies in hydrodynamical
simulations with restricted models of feedback
\cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation
efficiency \cite{Abadi} and the history of formation may also
determine the extent of this rounding.

@@

These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ varied between
$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
  is defined as the mass enclosed within the virial radius $R_{200}$
  at which the density becomes 200 times the critical density of the
  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
with the (AREPOOO HERE) by increasing the mass resolution of the
particles belonging to them and diminishing the resolution of the rest
of the particles.

Various versions of each halo were modelled with different degrees of
realism. All 30 halos were simulated within a level-4-degree of
resolution defined for Aquarius simulations corresponding to $\tilde
3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
M_\odot$. The principal details of each of these halos are consigned
on the table \ref{tab:level4}. From these halos, 6 of them where
re-simulated at level 3 (higher) resolution taking into account a
spatial factor of 2 in each dimension. For more information about
level 3 halos, their details are printed on table
\ref{tab:level3}. Furthermore, fore each halo in each level of
resolution there are two versions of the simulation. One of tracks the
evolution of DM-only particles while the remaining one evolves DM and
baryions with magneto-hydrodynamical (MHD) physics, including DM.

@@

There is no trivial way to calculate the DM halo shape at a determined
radius due to the discretization of particles. For practical effects,
observational models focus on the shape of the DM isopotential
\cite{isopotential} or isodensity \cite{isodensity} contours. In
cosmological simulations, it is preferred to work with the isodensity
contours which is directly calculated from particle
positions. However, these density contours are not smooth and are very
sensitive to the presence of small satelites \cite{Springel
  Isodensity}. For this reason we determine the shape taking into
account volume-enclosed particles, rather than shell-enclosed. While
this approach allows the cumulative influence of outter shells on the
outter shapes, it has been demonstrated for DM-only simulations that
this effect becomes important only for big radii \cite{vera-Ciro
  aquarius}.  We therefore follow the method of \cite[Allgood et
  al. 2006]{Allgood_et_al._2006} that consits in the use of the
reduced inertia tensor,

@@

The diagonalization of this tensor yields the principal axes of the
structure as well as the eigen-quantities which are proportional to
the squared principal axes $a>b>c$. We start our calculations taking
into account particles within a sphere of radius $R$ and then
recharacterize the triaxial parameters by taking into account
particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted
distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$
are the previously calculated axial ratios. We repeat this process
until the average deviation of semi-axes is less than $10^{-6}$.

\section{Results}
For convergence reasons and seeking to make our results
observation-comparable, we restrict the sampling of the ellipsoidal
parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial
radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS). All
our results make use of this reference radius unless strictly stated
otherwise.

\subsection{The radial tendency of axial ratios}
To have a more complete picture about the effect of baryons on the DM
halo shape, we begin by verifying/understanding the radial evolution
(dependence?) of the shape. In the case of DM-only simulations, it is
expected that halos get monotonically rounder at larger radii due to
(the gravitational effect of inner shells?) \citep{Vera-Ciro et
  al. 2012}. A graphic example of this rounding can be checked on
figure \ref{fig:slices}, where we plot the a projection of a DM-only
halo aligned with the calculated minor axis at two different radius
together with the estimated projected ellipsoidal. Formally, this
effect is reflected in the axial ratios $b/a,c/a$, which tend to unity
on the outerskirts of the halo. As a representative sample of this
relations, we show on figure \ref{fig:DM relation} the evolution, for
a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.

@@

We found that most halos exhibit a monotonically-increasing somewhat
steady tendency of its axial ratios $b/a,c/a$  with radius, which is
well exemplified on figure \ref{fig:DM_MHD}. There are some special
cases in which fluctuations of the local DM density field affects this
relation, but in average, this monotonic and steady tendency is clear
and can be consulted on table \ref{table:DM table}. To ilustrate the
average behavior, as well as some peculiarities, we resume the results
of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where
each shape represents a point in the triaxiality plane $c/a$ Vs
$b/a$. Check Vera-ciro onthis.

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  \cite{disk stability}. However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

@@

As a check of consistency, we compare our new isopotential shape
results with the analytic expression of the
$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine
  year]{Binney and tremaine}, taking the volume-enclosed axial ratios
as an approximation for the isodensity contour ratios
$q_{\rho}$. Although this analytic expression if meant to be used for
logarithmic axisymmetric halos, it works well as a first approximation
for nearly axisymmetric halos as those produced by our disced
galaxies. We find that the difference between the real and the
analytic isopotential axial ratios is not bigger than $quantity
percent$. With this, we may now present on table
\ref{tabe:isopotential} our observationally-comparable results for MHD
halos at two important radii one corresponding to the approximate
regimes where the MW DM halo is usually constrained.

Little discussion: Are our results congruent with observations? at
which radii, does the DM halo shape vary that much?. Which models are
favored?

@@

From the previous characterization of radial shapes it is clear that
MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at
every sampled radii. This can be compared on tables \ref{tabe:DM
  table} and \ref{tabe:MHD table} or at the representative example on
figure \ref{fig:DM_MHD}. From there, it is also noticeable that the
rounding effect of baryons is stronger at the disk regime, where the
DM halo is almost perfectly oblate. Furthermore, MHD halos tend
towards more oblate shapes (T < 0.5) despite DM halos tendency towards
more prolate shapes (T>0.5).

This rounding effect is expected from the gravitational effect of the
flattened axisymmetric galactic disk. It is also reasonable that this
effect is not as strong at $\approx 100$Kpc, where the disk potential
is dimmer compared to the DM halo potential. Keeping this in mind, one
would expect that the rounding effect of baryons is related to some
galactic parameters such as its component masses and radii. However,
even for the parameter of highest correlation with this rounding
effect (the baryonic fraction), the relation is not clear nor
conclusive due to the dispersion from galaxy peculiarities. In figure
\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
baryonic fraction of each galaxy. Although some linear tendency is
suggested qualitatively, the dispersion of the sample is very high to
obtain some conclusive relation. This is an evidence that
adiabatic-contraction models are not realistic as they may neglect
some effects of the galaxy evolution in the whole cosmological
context.

@@

Although the effect of the baryonic disk on the shape of the DM halo
is a reasonable explanation for the rounding effect, it does not
actually explain the deviation from oblateness of MHD halos at
$r<10$Kpc. In other words, if the disk is perfectly axisymmetric,
there must be some source of triaxiality at $r<10$Kpc to explain the
low axial ratios.

\textit{ Talk about source of triaxiality at the inner parts of the
  halos (bar?). This source of triaxiality at the inner parts explains
  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
  should also discuss that the decrease in the axial ratios for bigger
  radii may actually be bigger/steeper but it is dimmed by the
  contribution of inner parts.} 
%
%\begin{figure}
%  \centering
%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
%  \hfill
%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
%  \hfill
%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$. Each dot represents a halo shape at some radius. Some observational constraints are plotted alongside our results. Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space. caption replaces title.  Present constraints representation of density)}
%  \label{fig:Triaxiality_Inner_Outer}
%\end{figure}

\subsection{The historical shape}
One of the principal motivations to study the radial dependence of the
DM halo shape is that it may encode some clues about its formation
history. We have already shown that DM-only halos seem to exhibit a
steady and monotonous growth in its axial ratios when sampled at
bigger radii. One similar effect can be found if we sample the shape
at the virial radius, this time at varying redshift. It is easy to see
that the axial ratios increase with decreasing redshift, which is
expected by the continuous influence of the gravitational potential
\cite{VeraCiro}. In figure \ref{fig:RedshiftGood} we present a
representative example.

@@

Interestingly, these two parametic plots i.e. $(b/a,c/a)(z=0,r)$ and
$(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos
\ref{fig:DM Z Triax}. This means that, for DM-only halos, one can
approximate its shape at higher redshift by simply sampling its
current shape at a smaller radius \textbf{wording}. This relationship
relies strongly on the steady and monotonous tendency of DM halos
towards sphericity for bigger radii and smaller redshift.

@@

MHD halos, on the other hand, do not exhibit tendency towards
sphericity with bigger radii, but they do get sistematically rounder
at lower redshift as seen in figure \ref{fig:RedshiftGood}. This
effectively vanishes this correlation as seen from a DM halo
\ref{fig:MHD Z Triax}.

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs
      Star Density of the simulation.} 
    \label{fig:MHD Z Triax} 
\end{figure}

@@

One of the principal assumptions of observational models of the MW's
DM halo is that its minor axis is perfectly aligned with the disk
axis. Although this is a reasonable assumption to guarantee the
stability of the galactic disk in simplified models of isolated
galaxies, it may not be the case for galaxies evolved in the whole
cosmological context nor at every radii at which the shape is
sampled.

Therefore, it is of special interest to us to examin the strength of
this alignment assumption in the context of simulations. For this
purpose, we sampled the shape at 5 different radii and plotted the
axial directions, as well as the disk direction in the \textbf{name}
diagrams \cite{} (explain diagrams). Explain disk direction
calculation.

@@

\section*{Acknowledgements}
This project has received funding from the European Union’s Horizon
2020 Research and Innovation Programme under the Marie
Sk\l{}odowska-Curie grant agreement No 734374.
